Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Future work.

\paragraph{TCP payload length}
Figure \ref{fig:len} shows the payload size distribution of normal traffic and meek's traffic. Both
figures exhibit a significant amount of packets with no payload. These packets are mostly TCP SYN and ACK
packets. Figure \ref{fig:len:lbl} shows the distribution of normal traffic, which indicates a large portion
of small-sized packets. However, in the meek's traffic shown in Figure \ref{fig:len:meek}, most packets
are large packets ranging from 1400 bytes to 1500 bytes. This result is unexpected, because the underlying packets 
in the TLS session are sent from Tor. By default, each Tor cell is 512 bytes, but meek changes the packet size 
distribution. Therefore, meek provides traffic shaping without additional efforts.

@@

\paragraph{Concurrent connections}
Figure \ref{fig:connections} shows how many HTTPS connections to Google did a user make 
during the 10-minute measurement window.
There are 34,732 connections in total from 2,745 unique IPs. We observe that the majority of users have less than 
50 connections to the Google frontend server, and most of the numbers concentrate on 1 ~ 10. This is not unexpected
because a typical pattern of using Google is using the Google search as a stepping stone for other websites.

We measure the number of concurrent HTTPS connections during the automated browsing of Alexa
top 500 sites using three platforms: Tor Browser Bundle, Safari + Firefox extension, and Safari + Chrome extension.
Figure \ref{fig:conconns} shows the number over time. We can see that most of the time
the browser has one HTTPS connection to Google. Sometimes the browser may have more than one connection
due to background activities such as statistics reporting. In all cases the number of connections is always 
less than 5. We can conclude that the number of concurrent connections does not show distinct characteristics, as 
a small number of connections can be considered as a normal behavior.

@@

\paragraph{Connection lifetime}
We consider the connection lifetime as a potential weakness. Figure \ref{fig:duration:lbl} shows the 
connection lifetime distribution of normal traffic. Interestingly we can see the concentration on 
several discrete values: 60s, 120s, 180s, 240s. We hypothesize that it is due to the HTTP Keep-Alive 
timeout of different browsers and web services. Another important observation is the concentration on 
durations that exceed 600 seconds. Note that our trace only contains 10 minutes' data, therefore the concentration 
on 600 seconds does not reflect that these connections' actual duration is 600 seconds. Rather, 600 seconds
is the lower bound of their actual duration. Thus, we can conclude that only about 10\% connections last 
longer than 600 seconds.

The distribution of meek's traffic, in contrast, is totally different. First, there are much fewer connections, which is 
consistent with the discussions above. Second, the durations are much longer if we notice the x-axis in Figure \ref{fig:duration:meek}. If there is not a case in which normal users also have such long connections when browsing Google, the 
censor can potentially block any long connections between users and Google. Even if this is the case, the
censor has to wait until a time threshold is reached. The user might have already obtained the forbidden data she wants, or 
meek could simply restart a connection.

@@

% Pipelining of requests.
% Put a diagram here showing serialized requests.
% Simple reliability layer, SEQ/ACK.
% Would be useful for Iran-like session cutoff, independent of meek.

% Performance measurements

>>>>

\paragraph{TCP payload length}
Figure ~\ref{fig:len} shows the payload size distribution of normal traffic and meek's traffic. Both
figures exhibit a significant amount of packets with no payload. These packets are mostly TCP SYN and ACK
packets. Figure ~\ref{fig:len:lbl} shows the distribution of normal traffic, which indicates a large portion
of small-sized packets. However, in the meek's traffic shown in Figure ~\ref{fig:len:meek}, most packets
are large packets ranging from 1400 bytes to 1500 bytes. This result is unexpected, because the underlying packets 
in the TLS session are sent from Tor. By default, each Tor cell is 512 bytes, but meek changes the packet size 
distribution. Therefore, meek provides traffic shaping without additional efforts.

@@

\paragraph{Concurrent connections}
Figure ~\ref{fig:connections} shows how many HTTPS connections to Google did a user make 
during the 10-minute measurement window.
There are 34,732 connections in total from 2,745 unique IPs. We observe that the majority of users have less than 
50 connections to the Google frontend server, and most of the numbers concentrate on 1 ~ 10. This is not unexpected
because a typical pattern of using Google is using the Google search as a stepping stone for other websites.

We measure the number of concurrent HTTPS connections during the automated browsing of Alexa
top 500 sites using three platforms: Tor Browser Bundle, Safari + Firefox extension, and Safari + Chrome extension.
Figure ~\ref{fig:conconns} shows the number over time. We can see that most of the time
the browser has one HTTPS connection to Google. Sometimes the browser may have more than one connection
due to background activities such as statistics reporting. In all cases the number of connections is always 
less than 5. We can conclude that the number of concurrent connections does not show distinct characteristics, as 
a small number of connections can be considered as a normal behavior.

@@

\paragraph{Connection lifetime}
We consider the connection lifetime as a potential weakness. Figure ~\ref{fig:duration:lbl} shows the 
connection lifetime distribution of normal traffic. Interestingly we can see the concentration on 
several discrete values: 60s, 120s, 180s, 240s. We hypothesize that it is due to the HTTP Keep-Alive 
timeout of different browsers and web services. Another important observation is the concentration on 
durations that exceed 600 seconds. Note that our trace only contains 10 minutes' data, therefore the concentration 
on 600 seconds does not reflect that these connections' actual duration is 600 seconds. Rather, 600 seconds
is the lower bound of their actual duration. Thus, we can conclude that only about 10\% connections last 
longer than 600 seconds.

The distribution of meek's traffic, in contrast, is totally different. First, there are much fewer connections, which is 
consistent with the discussions above. Second, the durations are much longer if we notice the x-axis in Figure ~\ref{fig:duration:meek}. If there is not a case in which normal users also have such long connections when browsing Google, the 
censor can potentially block any long connections between users and Google. Even if this is the case, the
censor has to wait until a time threshold is reached. The user might have already obtained the forbidden data she wants, or 
meek could simply restart a connection.

@@

In future work we would like to implement pipelining of requests,
so that more than one HTTP request can be outstanding at a time.
This would have better performance compared to the current system,
which serializes requests and responses in order to keep the
underlying TCP stream in order.
A system of sequence numbers and acknowledgments as used in OSS~\cite{oss}
could make this possible.
% Would be useful for Iran-like session cutoff, independent of meek.

% Performance measurements
We would like to do more quantitative performance measurements,
in order to measure the overhead in bandwidth and latency that meek has over plain Tor.
We have done informal tests, such as browsing YouTube,
but have not yet put numbers to our measurements.

% Load balancing
